Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-26 paper/main.tex
added functor commutative diagram

A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. Functors $\bm{F}: \mathcal{C}^{op} \rightarrow \mathcal{D}$ are called contravariant functors.

@@

The natural transformation composes with a functor such that the output is a compatible functor between the same categories 
\begin{equation}
  \label{eq:related-work:equivariance:natural-transform}
\begin{tikzcd}
  & {} \arrow[dd, "\alpha", Rightarrow, shorten=1.5em] &             \\
\mathcal{C} \arrow[rr, "F", bend left] \arrow[rr, "G"', bend right] &                                     & \mathcal{D} \\
  & {}                                  &            
\end{tikzcd}
\end{equation}
This means that $\alpha(F: \mathcal{C} \rightarrow \mathcal{D}) = G: \mathcal{C} \rightarrow \mathcal{D}$ commutes for any morphism $f:c\rightarrow c^{\prime}$ \cite{fongInvitationAppliedCategory2019}. A natural transform is a way to specify which functors between categories preserve the structure of the categories in the same manner. Arbitrary morphisms on sheaves are natural transforms \cite{SheafMathematics2021,bradleyWhatNaturalTransformation}.

@@

of sheaf functors 
\begin{equation}
  \label{eq:artist:sheaf_map}
  \vartistc: \sheafc_{\vindexc^*}(\dtotalc) \rightarrow \sheafc_{\vartistc}(\gtotalc)
\end{equation}
where each sheaf is a map from an open set in the graphic base space $\opensetg \subset \gbase$ into a set of sections of a fiber bundle over that open set.

Because the artist is a natural transform, it also transforms morphisms between functors\cite{bradleyWhatNaturalTransformation, maclaneCategoriesWorkingMathematician2013}. As illustrated in \autoref{eq:artist:morphism-of-sheaf-data}, the morphism between data sheaves is $\dfunc$. By definition of a natural transform, the following diagram commutes

>>>>

A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. For example, the functor $F:\mathcal{C} \rightarrow \mathcal{D}$ maps an object in $\mathcal{C}$ into an object in $\mathcal{D}$
\begin{equation}
\label{eq:related-work:equivariance:functor_diagram}
\begin{tikzcd}
  c \in Ob(\mathcal{C}) \arrow[d, "f"'] \arrow[r, "F"] & F(c) \in Ob(\mathcal{D}) \arrow[d, "F(f)"] \\
  c^{\prime} \in Ob(\mathcal{C}) \arrow[r, "F"]        & F(c^{\prime}) \in Ob(\mathcal{D})         
  \end{tikzcd} 
\end{equation}
 such that every morphism $f \in Hom(\mathcal{C})$ there is a compatible morphism $F(f) in Hom(\mathcal{D})$. Functors $\bm{F}: \mathcal{C}^{op} \rightarrow \mathcal{D}$ are called contravariant functors.

@@

The natural transformation composes with a functor such that the output is a compatible functor between the same categories 
\begin{equation}
  \label{eq:related-work:equivariance:natural-transform}
\begin{tikzcd}
  & {} \arrow[dd, "\alpha", Rightarrow, shorten=1.5em] &             \\
\mathcal{C} \arrow[rr, "F", bend left] \arrow[rr, "G"', bend right] &                                     & \mathcal{D} \\
  & {}                                  &            
\end{tikzcd}
\end{equation}
This means that $\alpha(F: \mathcal{C} \rightarrow \mathcal{D}) = G: \mathcal{C} \rightarrow \mathcal{D}$ commutes for any morphism $f:c\rightarrow c^{\prime}$ \cite{fongInvitationAppliedCategory2019}.Given a morphism $f: c\rightarrow c^{\prime}$ for $c, c^{\prime} \in Ob(\mathcal{C})$, the natural transformation decomposes into the components of the morphism $\alpha_{c}, \alpha_{c^{\prime}}$, which yields the naturality condition \cite{milewskiCategoryTheoryProgrammers} 
\begin{equation}
  \label{eq:related-work:equivariance:naturality-condition}
  G(f) \circ \alpha_{c} = \alpha_{c^\prime} \circ F(f)
\end{equation}

which can be expressed as the diagram commuting

\begin{equation}
  \label{eq:related-work:equivariance:natural-transform-components}
  \begin{tikzcd}
    c \arrow[dd, "f"'] &  & F(c) \arrow[dd, "F(f)"'] \arrow[rr, "\alpha_{c}"] &  & G(c) \arrow[dd, "G(f)"] \\
    {} \arrow[rr, shorten > = 5]      &  & {}                                                &  &                         \\
    c^{\prime}         &  & F(c^{\prime}) \arrow[rr, "\alpha_{c^{\prime}}"]   &  & G(c^{\prime})          
    \end{tikzcd}
\end{equation}

A natural transform is a way to specify which functors between categories preserve the structure of the categories in the same manner. Arbitrary morphisms on sheaves are natural transforms \cite{SheafMathematics2021,bradleyWhatNaturalTransformation}.

@@

of sheaf functors 
\begin{equation}
  \label{eq:artist:sheaf_map}
  \vartistc: \sheafc_{\vindexc^*}(\dtotalc) \rightarrow \sheafc_{\vartistc}(\gtotalc)
\end{equation}
where each sheaf is a map from an open set in the graphic base space $\opensetg \subset \gbase$ into a set of sections of a fiber bundle over that open set. As defined in \autoref{eq:related-work:equivariance:natural-transform}, the artist is a natural transformation. The artist has two components, a sheaf morphism $\vartist_{\openset}$ and a morphism $\vartist_{\Gamma}$ between sets of sections.

\begin{equation}
  \label{eq:artist:artist_gamma}
\end{equation}

As illustrated in \autoref{eq:artist:morphism-of-sheaf-data}, the morphism between data sheaves is $\dfunc$. By definition of a natural transform, the following diagram commutes
